Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-14 prop_iop.tex
prop_iop.tex \section{Quantum Real-valued and Interval-valued Probability Measures\label{sec:Real-and-Interval}} Fixing citations...

Although a convex interval-valued function\nb$\iota$ may look exotic,
its left end, defined by $\iotal\left(x\right)=\min\iota\left(x\right)$,
is well-studied Wright-convex satisfying $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$\nb\cite{Wright1954,RobertsVarberg1973,Pales2013}.
After we define interval-valued function, we are ready to construct
a QIVPM from a quantum probability measure.

@@

Since we cannot restrict our convex interval-valued function mapping
only finite number of intervals, let's consider another natural interval-valued
function. Before we consider them, we review the counterpart of Weight-convex,
Weight-concave\nb\cite{PecaricTong1992,Brzdek_2014}.

>>>>

Although a convex interval-valued function\nb$\iota$ may look exotic,
its left end, defined by $\iotal\left(x\right)=\min\iota\left(x\right)$,
is well-studied Wright-convex satisfying $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$\nb\cite{Wright1954,RobertsVarberg1973,PecaricTong1992}.
After we define interval-valued function, we are ready to construct
a QIVPM from a quantum probability measure.

@@

Since we cannot restrict our convex interval-valued function mapping
only finite number of intervals, let's consider another natural interval-valued
function. Before we consider them, we review the counterpart of Wright-convex,
Wright-concave\nb\cite{Brzdek_2014}.
